Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-01 Draft/Draft.Rmd
Probando sin color

Here, we used ... blah... and fined plant functional groups by using a comprehensive dataset with several reproductive traits and pollinator functional groups as the main differentiated guilds in life form and behaviour. Then, we explored the main motifs of these networks and we found [...]

@@

We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019]. To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.

@@

ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
  geom_histogram(color="black", fill="white")+
  facet_wrap(~position)+
  theme_bw()+
  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")

ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
  geom_histogram(color="black", fill="white")+
  facet_wrap(~position)+
  theme_bw()+
  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")

>>>>

Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant species into functional groups that represented different reproductive strategies by using a comprehensive dataset with several floral, reproductive and vegetative traits. In addition, we classified pollinator species based on life form and bevavior into different functional groups. Then, we used explored the general patterns of motifs in these plant-pollinator networks

plant functional groups by using a comprehensive dataset with several reproductive traits and pollinator functional groups as the main differentiated guilds in life form and behaviour. Then, we explored the main motifs of these networks and we found [...]

@@

We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019]. To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1. Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite plant-pollinator networks", fig.width=10,fig.height=8}
library(tidyverse)
library(RColorBrewer)
source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")

motif_number <- 1
p1 <- plot_motif_positions(motif_number)

motif_number <- 2
p2 <- plot_motif_positions(motif_number)

motif_number <- 3
p3 <- plot_motif_positions(motif_number)

motif_number <- 4
p4 <- plot_motif_positions(motif_number)

motif_number <- 5
p5 <- plot_motif_positions(motif_number)

motif_number <- 6
p6 <- plot_motif_positions(motif_number)

motif_number <- 7
p7 <- plot_motif_positions(motif_number)

motif_number <- 8   
p8 <- plot_motif_positions(motif_number)

motif_number <- 9
p9 <- plot_motif_positions(motif_number)

motif_number <- 10
p10 <- plot_motif_positions(motif_number)

motif_number <- 11
p11 <- plot_motif_positions(motif_number)

motif_number <- 12
p12 <- plot_motif_positions(motif_number)

motif_number <- 13
p13 <- plot_motif_positions(motif_number)

motif_number <- 14
p14 <- plot_motif_positions(motif_number)

motif_number <- 15
p15 <- plot_motif_positions(motif_number)

motif_number <- 16
p16 <- plot_motif_positions(motif_number)

motif_number <- 17
p17 <- plot_motif_positions(motif_number)

library(patchwork)

(p1 & ylab("2 species")| p2 & ylab("3 species") | p3 )/ (p4 & ylab("4 species")| p5 | p6 | p7)/ (p8  & ylab("5 species")| p9 | p10 | p11 | p12) / (p13 & ylab("5 species")| p14 | p15 | p16 | p17)+
 plot_annotation(tag_levels = '1') & theme(axis.title.y = element_text(color="black", size=14, face="bold"))

@@

#ggplot(plant_position_percentiles_filtered, aes(percentil_its_GF))+
#  geom_histogram(color="black", fill="white")+
#  facet_wrap(~position)+
#  theme_bw()+
#  labs(x="Sizeclass percentile", title = "Histograms: Percentiles for plant positions")
#
#ggplot(pollinator_position_percentiles_filtered, aes(percentil_its_GF))+
#  geom_histogram(color="black", fill="white")+
#  facet_wrap(~position)+
#  theme_bw()+
#  labs(x="Sizeclass percentile",title = "Histograms: Percentiles for pollinator positions")
#
